Comparison of CORD-19-trained GPT-2-based Chatbot Responses Across Different Text Semantic Similarity Approaches

### 2020-04-11 paper/paper.tex
Added annotation guidelines

For evaluating the performance of the approaches, we chose 12 different
questions. For each approach, we generated 5 different answers for the same
question, resulting in the total of 240 answers. We then asked experienced
medical personnel at Mayo Clinic to rate these answers. The questions are
presented below.

\begin{itemize}
  \item Are there geographic variations in the mortality rate of COVID-19?
  \item What is known about transmission, incubation, and environmental stability of COVID-19?
  \item Is there any evidence to suggest geographic based virus mutations of COVID-19?
  \item Are there geographic variations in the rate of COVID-19 spread?
  \item What do we know about virus genetics, origin, and evolution of COVID-19?
  \item What has been published about ethical and social science considerations of COVID-19?
  \item What has been published about medical care of COVID-19?
  \item What do we know about diagnostics and surveillance of COVID-19?
  \item What do we know about COVID-19 risk factors?
  \item What has been published about information sharing and inter-sectoral collaboration of COVID-19?
  \item What do we know about vaccines and therapeutics of COVID-19?
  \item What do we know about non-pharmaceutical interventions of COVID-19?
\end{itemize}

>>>>

For evaluating the performance of the approaches, we chose 12 different
questions (presented below).

\begin{itemize}
  \item Are there geographic variations in the mortality rate of COVID-19?

  \item What is known about transmission, incubation, and environmental
        stability of COVID-19?

  \item Is there any evidence to suggest geographic based virus mutations of
        COVID-19?

  \item Are there geographic variations in the rate of COVID-19 spread?

  \item What do we know about virus genetics, origin, and evolution of
        COVID-19?

  \item What has been published about ethical and social science considerations
        of COVID-19?

  \item What has been published about medical care of COVID-19?

  \item What do we know about diagnostics and surveillance of COVID-19?

  \item What do we know about COVID-19 risk factors?

  \item What has been published about information sharing and inter-sectoral
        collaboration of COVID-19?

  \item What do we know about vaccines and therapeutics of COVID-19?

  \item What do we know about non-pharmaceutical interventions of COVID-19?
\end{itemize}

\noindent For each approach, we generated 5 different answers for the same
question, resulting in the total of 240 answers. We then asked experienced
medical personnel at Mayo Clinic to rate these answers. The rating system was
composed of 5 different scores:

\begin{itemize}
  \item	Relevant --- the answer partially or fully answers the question and/or
        makes clear attempts to do so and is related to the question.
        (5 points)

  \item	Well-formed --- the answer makes a logical sense and is somewhat
        related to both the question and COVID-19, yet it does not (partially
        or fully) answer the question.
        (4 points)

  \item	Informative --- the answer is not related to the question, but provides
        some information about COVID-19 and makes a logical sense.
        (3 points)

  \item	Acceptable --- the answer makes some logical sense and is weakly
        related to the question or COVID-19, but is mostly difficult to
        understand.
        (2 points)

  \item	Poor --- the answer is totally unrelated to the question or COVID-19
        and/or does not make a logical sense.
        (1 point)
\end{itemize}
